Detecting Stylistic Variation in Pop Production

### 2023-12-05 outputs/paper/paper.qmd
fixing appendix

lr_data %>%
  select(-producer,-tempo,-loudness,-mode) %>%
  pivot_longer(cols = -is_antonoff,
               names_to = "feature",
               values_to = "value") %>%
  ggplot(aes(
    x = feature,
    y = value,
    fill = factor(is_antonoff)
  )) +
  geom_boxplot(alpha = 0.6, position = position_dodge(width = 0.8)) +
  scale_fill_manual(values = c("#B0C4DE", "#9ACD32"),
                    labels = c("No", "Yes")) +
  theme_minimal() +
  labs(fill = "Antonoff", x = "Feature", y = "Value") +
  coord_flip()  
```)

>>>>

lr_data %>% 
  select(-producer,-tempo,-loudness,-mode) %>% 
  pivot_longer(cols = -is_antonoff, names_to = "feature", values_to = "value") %>% 
  ggplot(aes( x = feature, y = value, fill = factor(is_antonoff) )) +
  geom_boxplot(alpha = 0.6, position = position_dodge(width = 0.8)) +
  scale_fill_manual(values = c("#B0C4DE", "#9ACD32"), labels = c("No", "Yes")) + 
  theme_minimal() + 
  labs(fill = "Antonoff", x = "Feature", y = "Value") + 
  coord_flip()
```
